The value of intermediation

### 2022-09-13 src/presentation/presentation.qmd
Update the skeleton of the presentation

---
title: "The value of intermediation"
author: "Martin Stancsics"
format:
    revealjs:
        embed-resources: true
        transition: fade
bibliography: references.bib
---

@@

#

@@

# The relevant setting

@@

Shapley value:
$$
\scriptsize
\varphi_P^n(f) = \frac{1}{n+1} \sum_{k=0}^{n} f(k)
$$
::: {.fragment .fade-in fragment-index=4}
$$
\scriptsize
\to \int_0^1 f(t) \, \mathrm{d}t
$$
:::

@@

$$
\lim_{n \to \infty} \phi_P^n(f) = \int_0^1 f(t) \, \mathrm{d}t
$$
:::

@@

# Thank you

>>>>

---
title: "The value of intermediation"
author: "Martin Stancsics"
format:
    revealjs:
        embed-resources: true
        transition: fade
        toc: true
        toc-depth: 1
        toc-title: Agenda
bibliography: references.bib
---

@@

# The Shapley-value

@@

# Main results

@@

::: {.fragment .fade-in fragment-index=2}
Shapley value:
$$
\scriptsize
\varphi_P^n(f) = \frac{1}{n+1} \sum_{k=0}^{n} f(k)
$$
:::
::: {.fragment .fade-in fragment-index=4}
$$
\scriptsize
\to \int_0^1 f(t) \, \mathrm{d}t
$$
:::

@@

$$
\lim_{n \to \infty} \varphi_P^n(f) = \int_0^1 f(t) \, \mathrm{d}t
$$
:::

@@

# Extensions

## Multiple platforms

## Weighted value

# Example application

## Market setup

## Timing of the game

## Results

# Conclusion

## Conclusions

 - Proposed a very tractable way of modeling bargaining applicable to certain important contexts
 - The results are for upstream-downstream situations, platform settings, and two-sided markets
 - The outcomes generally concur with intuitive expectations
 - Even the simple example application provides some interesting insights into hybrid platforms

## Future work

- There is a variety of ways in which the model could be extended (e.g. additional platforms provide some value)
- The example application could be turned into a proper, full-fledged model
- A lab experiment about the outcomes of group bargaining could be conducted
- The model could be applied to other contexts

# Thank you {.unnumbered .unlisted}
